### 2020-03-23 6_related.tex
Tweaks to avoid stray words.

Parallel and distributed programming systems are most
commonly evaluated using proxy- or mini-apps, or
microbenchmarks. Mini-apps are explicitly derived from larger
applications and therefore have the advantage of bearing some
relationship to the original. This advantage typically does not hold
for microbenchmarks.

@@

\item
The initial paper on PENNANT~\cite{PENNANT} includes an
implementation that supports MPI/OpenMP/MPI+OpenMP; follow-up papers present an implementation in
Regent~\cite{Regent15, ControlReplication17, LegionTracing18}.

@@

\item
A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, and of those three only two can be compared in an
apples-to-apples manner as the last implementation uses a structured
rather than an unstructured mesh. Follow-up papers describe an
additional implementation in Regent~\cite{Regent15,
  ControlReplication17, LegionTracing18} (comparison against reference
only).

@@

Microbenchmarks can be easier to implement, but risk being
unrepresentative of real applications. PRK Stencil~\cite{PRK14}
contains 2 kernels (which combined fit in under 50 lines of C++)
and a halo exchange on a structured grid; an
evaluation~\cite{PRKRuntimes16} compares MPI variants, SHMEM, UPC,
Charm++, and Grappa. The NAS benchmark suite~\cite{NAS91, NAS95}
consists mostly of small kernels for dense array computations and has
implementations in OpenMP~\cite{NASOpenMP99}, MPI and
MPI+OpenMP~\cite{NASMPIOpenMP00}, and
Charm++~\cite{NASCharm96}. Neither PRK nor NAS achieve the breadth of
coverage, flexibility, or ease of implementation of Task Bench. We
believe the evidence for ease of implementation is clear; Task Bench
is implemented for more systems than all previous mini-apps and
microbenchmarks. Task Bench is also not a fixed set of benchmarks, and
it is even easier to use Task Bench to generate new benchmarks.

>>>>

Parallel and distributed programming systems are often
evaluated using proxy- or mini-apps, or
microbenchmarks. Mini-apps are explicitly derived from larger
applications and hence have the advantage of bearing some
relationship to the original. This advantage typically does not hold
for microbenchmarks.

@@

\item
The PENNANT reference implementation supports
MPI/OpenMP/MPI+OpenMP~\cite{PENNANT}. A follow-up paper presents a
Regent implementation~\cite{Regent15}.

@@

\item
A report on MiniAero~\cite{SandiaReportManyTaskRuntimes15} describes
four implementations of the mini-app, but only includes performance
results for three, and of those three only two can be compared in an
apples-to-apples manner as the last implementation uses a structured
rather than an unstructured mesh. A follow-up paper describes another
implementation in Regent~\cite{Regent15} (comparison against reference
only).

@@

Microbenchmarks can be easier to implement, but risk being
unrepresentative of real applications. PRK Stencil~\cite{PRK14}
contains 2 kernels (which combined fit in under 50 lines of C++)
and a halo exchange on a structured grid; an
evaluation~\cite{PRKRuntimes16} compares MPI variants, SHMEM, UPC,
Charm++, and Grappa. The NAS benchmark suite~\cite{NAS91, NAS95}
consists mostly of small kernels for dense array computations and has
implementations in OpenMP~\cite{NASOpenMP99}, MPI and
MPI+OpenMP~\cite{NASMPIOpenMP00}, and
Charm++~\cite{NASCharm96}. Neither PRK nor NAS achieve the breadth of
coverage, flexibility, or ease of implementation of Task Bench. We
believe the evidence for ease of implementation is clear; Task Bench
is implemented for more systems than all previous mini-apps and
microbenchmarks. Task Bench is also not a fixed set of benchmarks, and
makes it easy to generate new benchmarks.
